---
title: "Parviflora_MonthlySales"
author: "Group"
date: "07/06/2020"
output:
  
  ioslides_presentation: default
  beamer_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
pacman::p_load(pacman,tidyverse,stringr,readr,readxl,lubridate,stringi,zoo)
source("mung.R")
library(knitr)
library(gridExtra)

# Data Import ----

fileList <- list.files("data/", full.names = TRUE)
summary_fileList <- as.list(fileList[str_detect(fileList, "Summary of Sales")])
sheets_titles <- as.list(excel_sheets(fileList[str_detect(fileList, "Daffodils")]))


store_index <- read_excel(fileList[str_detect(fileList, "Stores")])
summaries   <- lapply(summary_fileList, summary_import, loc_index = store_index)
daffodils   <- lapply(sheets_titles, daffodils_import, fileList = fileList)

daffo_aggr  <- lapply(daffodils, daffodils_aggregator)

merged      <- lapply(summaries, merger, daffo_aggr)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Quick facts

- Analyzed period: `r date_v = c()
for (x in 1:length(summary_fileList)){
date = gsub("([A-z])(\\d)", "\\1 \\2", merged[[x]][[2]])
date_v = c(date_v, date)
}
date_df = data.frame(date=date_v)
date_df$date = as.yearmon(date_df$date, format = '%b %y')
paste0(min(date_df$date)," - ", max(date_df$date))`
- Total sales in Q1: `r  total = 0
for (x in 1:length(summary_fileList)) { subsum = sum(merged[[x]][[1]][,'TOTAL_VALUE'])
total = total + subsum}
total`
- 
- Bullet 3

## Top locations trend

```{r, echo = FALSE, }
top_locations(5)
```

##  

```{r, echo = FALSE, }
grid.arrange(
monthly_single('AZALEA_TOTAL'),
monthly_single('BEGONIA_TOTAL'),
monthly_single('CARNATION_TOTAL'),
monthly_single('DAFFODIL_TOTAL'),
ncol=2, nrow =2)

```

## Slide with Plot

```{r pressure}
plot(pressure)
```

