---
title: "Parviflora Monthly Report"
author: "Pawel Bagniuk, Nikita Batsenko, Wojciech Pierzchala, Piotr Sokol"
date: "10/06/2020"
output:
  
  ioslides_presentation: default
  beamer_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
pacman::p_load(pacman,tidyverse,stringr,readr,readxl,lubridate,stringi,zoo,scales,knitr,gridExtra)
source("src.R")
```

## Data overview

- Analyzed period: `r date_v = c()
for (x in 1:length(summary_fileList)){
date = gsub("([A-z])(\\d)", "\\1 \\2", merged[[x]][[2]])
date_v = c(date_v, date)
}
date_df = data.frame(date=date_v)
date_df$date = as.yearmon(date_df$date, format = '%b %y')
paste0(min(date_df$date)," - ", max(date_df$date))`
- Total number of transactions: `r total = 0
for (x in 1:length(summary_fileList)) { subsum = sum(merged[[x]][[1]][,'TOTAL_COUNT'])
total = total + subsum}
format(total, scientific = NA, big.mark = ' ')`
- Total sales: `r total = 0
for (x in 1:length(summary_fileList)) { subsum = sum(merged[[x]][[1]][,'TOTAL_VALUE'])
total = total + subsum}
format(total, scientific = NA, big.mark = ' ')`
- Daffodils Retail Sales: `r total = 0
for (x in 1:length(summary_fileList)) { subsum = sum(merged[[x]][[1]][merged[[x]][[1]]$RETAIL == 1,'DAFFODIL_TOTAL'])
total = total + subsum}
format(total, scientific = NA, big.mark = ' ')`
- Daffodils Gross Sales: `r total = 0
for (x in 1:length(summary_fileList)) { subsum = sum(merged[[x]][[1]][merged[[x]][[1]]$GROSS == 1,'DAFFODIL_TOTAL'])
total = total + subsum}
format(total, scientific = NA, big.mark = ' ')`
- Share of daffodil sales: `r total = 0
for (x in 1:length(summary_fileList)) { subsum = sum(merged[[x]][[1]][,'TOTAL_VALUE'])
total = total + subsum}
total

daffodils_total = 0
for (x in 1:length(summary_fileList)) { subsum = sum(merged[[x]][[1]][,'DAFFODIL_TOTAL'])
daffodils_total = daffodils_total + subsum}
 label_percent(0.01)(daffodils_total/total)`
- Share of azalea sales: `r total = 0
for (x in 1:length(summary_fileList)) { subsum = sum(merged[[x]][[1]][,'TOTAL_VALUE'])
total = total + subsum}

azalea_total = 0
for (x in 1:length(summary_fileList)) { subsum = sum(merged[[x]][[1]][,'AZALEA_TOTAL'])
azalea_total = azalea_total + subsum}
 label_percent(0.01)(azalea_total/total)`
- Share of begonia sales: `r total = 0
for (x in 1:length(summary_fileList)) { subsum = sum(merged[[x]][[1]][,'TOTAL_VALUE'])
total = total + subsum}

begonia_total = 0
for (x in 1:length(summary_fileList)) { subsum = sum(merged[[x]][[1]][,'BEGONIA_TOTAL'])
begonia_total = begonia_total + subsum}
 label_percent(0.01)(begonia_total/total)`
- Share of carnation sales: `r total = 0
for (x in 1:length(summary_fileList)) { subsum = sum(merged[[x]][[1]][,'TOTAL_VALUE'])
total = total + subsum}

carnation_total = 0
for (x in 1:length(summary_fileList)) { subsum = sum(merged[[x]][[1]][,'CARNATION_TOTAL'])
carnation_total = carnation_total + subsum}
 label_percent(0.01)(carnation_total/total)`


## Top locations sales trend

```{r, echo = FALSE, }
top_locations(5)
```

## Flowers sales trend

```{r, echo = FALSE, }
grid.arrange(
monthly_single('AZALEA_TOTAL'),
monthly_single('BEGONIA_TOTAL'),
monthly_single('CARNATION_TOTAL'),
monthly_single('DAFFODIL_TOTAL'),
ncol=2, nrow =2)

```

## Daffodil sales by location

```{r, echo = FALSE, }
df <- merged[[1]][[1]]
df_final = df

for (x in 2:length(summary_fileList)){
  df <- merged[[x]][[1]]
  df_final <- rbind(df_final, df)
}

df_final <- df_final[,c('LOCATION','DAFFODIL_TOTAL','DAFFODIL_COUNT')]
df_final_agg = aggregate(.~LOCATION, data = df_final, FUN = sum)

df_final_agg = df_final_agg %>% mutate(DAFFODIL_TOTAL = (DAFFODIL_TOTAL)/length(summary_fileList), DAFFODIL_COUNT = (DAFFODIL_COUNT)/length(summary_fileList))

df_final_agg$Avg_transaction_value <- with(df_final_agg, DAFFODIL_TOTAL/DAFFODIL_COUNT)

df_final_agg = df_final_agg[order(-df_final_agg[,'Avg_transaction_value']),]

df_final_agg = df_final_agg[!(df_final_agg$LOCATION == 'MISSING'),]

plot <- ggplot(df_final_agg, aes(x = reorder(LOCATION, -DAFFODIL_TOTAL),  y = DAFFODIL_TOTAL))+
  geom_bar(stat="identity",position=position_dodge2(), fill='steelblue') + 
  xlab('LOCATION')+
  ylab('REVENUE')+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5), axis.title.y= element_blank())+
  ggtitle('Average Monthly Daffodil Sales by Location')
plot
```

## Things to improve from next month
<font size = '5'> Summaries </font> <br>
<font size ='4'>
- not-hashed Polish signs - encoding  <br>
- standardized file length  <br>
- unique column names - count columns  <br>
</font>

<font size = '5'> Daffodils </font> <br>
<font size ='4'>
- no other IDs than in Stores - e.g. ID 345 <br>
- unified submitting location forms - strange record in March <br>
</font>

<font size = '5'> Stores </font> <br>
<font size ='4'>
- unified store names - Swiebodzin <br>
- complete list of stores <br>
</font>

<font size = '5'> All </font> <br>
<font size ='4'>
- unified store IDs - same number of digits <br>
- established categories for recording sales - e.g. gross/retail/other <br>
</font>




